### 2023-03-20 chapter0/chapter0.tex
Replaced dramatic with large to sound less sensational

In contrast, IDRs have no fixed spatial relationship between their atoms, so their structures are sometimes described as conformational ensembles, \textit{i.e.} collections of conformations where the distances and orientations between residues can vary considerably. Furthermore, IDRs populate a continuum of structural states over time whereas when folded domains undergo dramatic conformational changes, they are usually triggered by specific environmental signals or chemical modifications, and the intermediate structures are transient. Despite the diversity of conformations available to IDRs, they can be broadly grouped into one of several qualitative descriptions which range from extended coils to more compact globules. The specific conformational class of a given IDR, however, is dictated by its local composition of amino acid residues. Because the chemical properties of each amino acid in the protein alphabet are dictated its specific arrangement of atoms, each has a unique impact on a protein's structure. However, to simplify discussion and analysis amino acids are often compared by quantitative factors like size or charge. One of the most useful scales for describing an amino acid's overall effect on protein structure is hydrophobicity, which measures a molecule's tendency to associate with water. Molecules which attract water are hydrophilic (water loving), and molecules which repel water are hydrophobic (water fearing). Hydrophilic molecules, like sugar or alcohol, easily dissolve in water whereas hydrophobic molecules, like fats and oils, remain separate. Since the cellular environment is largely water, the hydrophobic residues in proteins tend to aggregate into a hydrophobic core. This hydrophobic collapse is a major driving force in the early stages of protein folding, so a protein's relative number of hydrophilic and hydrophobic residues is a key determinant of whether it is folded or disordered.

>>>>

In contrast, IDRs have no fixed spatial relationship between their atoms, so their structures are sometimes described as conformational ensembles, \textit{i.e.} collections of conformations where the distances and orientations between residues can vary considerably. Furthermore, IDRs populate a continuum of structural states over time whereas when folded domains undergo large conformational changes, they are usually triggered by specific environmental signals or chemical modifications, and the intermediate structures are transient. Despite the diversity of conformations available to IDRs, they can be broadly grouped into one of several qualitative descriptions which range from extended coils to more compact globules. The specific conformational class of a given IDR, however, is dictated by its local composition of amino acid residues. Because the chemical properties of each amino acid in the protein alphabet are dictated its specific arrangement of atoms, each has a unique impact on a protein's structure. However, to simplify discussion and analysis amino acids are often compared by quantitative factors like size or charge. One of the most useful scales for describing an amino acid's overall effect on protein structure is hydrophobicity, which measures a molecule's tendency to associate with water. Molecules which attract water are hydrophilic (water loving), and molecules which repel water are hydrophobic (water fearing). Hydrophilic molecules, like sugar or alcohol, easily dissolve in water whereas hydrophobic molecules, like fats and oils, remain separate. Since the cellular environment is largely water, the hydrophobic residues in proteins tend to aggregate into a hydrophobic core. This hydrophobic collapse is a major driving force in the early stages of protein folding, so a protein's relative number of hydrophilic and hydrophobic residues is a key determinant of whether it is folded or disordered.
